Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-04-14 draft_p2.tex
Moves figure typical_drag_signal and description to part II.B. The Drag as a Random Process

% Description du signal de trainee typique
Figure~\ref{fig:typical_drag_signal} illustrates the time evolution of the drag acting on the square obstacle over a one thousands turnover times.
The signal appears unpredictable in details and exhibits repeated bursts of high amplitude that deviate significantly from the averaged value.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{typical_drag_signal/typical_drag_signal.png}
  \caption{Temporal evolution of the drag acting on the square under the action of the incident turbulent flow. The time is normalized by the turnover time related the mean-flow velocity and the size of the obstacle: $\tau_0=R/U$.}
  \label{fig:typical_drag_signal}
\end{figure}

@@

\begin{figure}
  \centering
    \subfloat[\ac{pdf} of drag fluctuations around mean.]
    {\label{fig:pdf_drag_a}
    	\includegraphics[width=.45\linewidth]{./PDF_drag/PDF_drag.png}}
    \subfloat[Autocorrelation of drag.]
    {\label{fig:pdf_drag_b}
    	\includegraphics[width=.45\linewidth]{./autocorr_drag/autocorr_drag.png}}  
      \caption{\textbf{(a)} Estimate of the zero-mean \ac{pdf} for drag fluctuations $f'_d = (f_d - \bar{f_d})$ where $\bar{f_d}$ denotes the averaged value. The drag is evaluated both in the presence and absence of the obstacle. Note that both \acsp{pdf} have different variance, and are here not normalized.
  \textbf{(b)} Autocorrelation function of the drag defined as $\left( \overline{f_d(t+\tau)f_d(t)}-\overline{f_d}^2 \right) /\sigma^2$. The lag $\tau$ is normalized by the turnover-time~\eqref{eq:turnover_time}.}
  \label{fig:pdf_drag}
\end{figure}

Fig.~\ref{fig:typical_drag_signal} illustrates the time evolution of the drag acting on the square obstacle.
The signal appears unpredictable in details and exhibits repeated bursts of high amplitude that deviate significantly from the averaged value.
It is therefore natural to model the drag as a scalar random process $f_d(t)$.

Drag fluctuations have been sampled along a long simulation of duration $T_{tot} = 4\times 10^6~\tau_0$, which will be referred to as the \textit{control run} in the following.
The \ac{pdf} of drag fluctuations deviates from a normal law and shows an exponential tail for large positive fluctuations, i.e.  ${\cal P}(f_d) = \lambda^{-1}e^{-\lambda f_d}$.
%
Fig.~\ref{fig:pdf_drag_a} also displays the \ac{pdf} of drag fluctuations acting on a control surface equivalent to the periphery of the obstacle but in the absence of the obstacle. 
%
In that case, the \ac{pdf} is quasi-symmetric and does not display exponential tails, indicating that the asymmetry of the \ac{pdf} and the development of positive exponential tail are closely related to the no-slip condition on the obstacle.
%
Lastly, the autocorrelation function of the drag is shown in Fig.~\ref{fig:pdf_drag_b}. It is found drag fluctuations are correlated over a time scale of the order of $\tau_0$, suggesting that the drag signal looses its memory typically after the sweeping of a few eddies past the obstacle.
%
This observation has important consequences for the application of rare event algorithms, as will be discussed in section~\ref{sec:rare_events_algorithms}.
%
In the following we define the \textit{correlation time} $\tau_c = 4\tau_0$.
Note that the ratio $tau_0 / tau_c$ may be viewed as a \textit{Strouhal number} $St$.
A value $St=0.25$ is consistent with commonly observed values for flows past blunt structures.

>>>>

@@

@@

% Description du signal de trainee typique
Fig.~\ref{fig:typical_drag_signal} illustrates the time evolution of the drag acting on the square obstacle.
The signal appears unpredictable in details and exhibits repeated bursts of high amplitude that deviate significantly from the averaged value.
It is therefore natural to model the drag as a scalar random process $f_d(t)$.
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{typical_drag_signal/typical_drag_signal.png}
  \caption{Temporal evolution of the drag acting on the square under the action of the incident turbulent flow. The time is normalized by the turnover time related the mean-flow velocity and the size of the obstacle: $\tau_0=R/U$.}
  \label{fig:typical_drag_signal}
\end{figure}

Drag fluctuations have been sampled along a long simulation of duration $T_{tot} = 4\times 10^6~\tau_0$, which will be referred to as the \textit{control run} in the following.
The corresponding estimate of the \ac{pdf} of drag fluctuations is shown in figure~\ref{fig:pdf_drag_a}.
It deviates from a normal law and shows an exponential tail for large positive fluctuations, \textit{i.e.}  ${\cal P}(f_d) = \lambda^{-1}e^{-\lambda f_d}$.
%
Fig.~\ref{fig:pdf_drag_a} also displays the \ac{pdf} of drag fluctuations acting on a control surface equivalent to the periphery of the obstacle but in the absence of the obstacle. 
%
In that case, the \ac{pdf} is quasi-symmetric and does not display exponential tails, indicating that the asymmetry of the \ac{pdf} and the development of positive exponential tail are closely related to the no-slip condition on the obstacle.
\begin{figure}
  \centering
    \subfloat[\ac{pdf} of drag fluctuations around mean.]
    {\label{fig:pdf_drag_a}
    	\includegraphics[width=.45\linewidth]{./PDF_drag/PDF_drag.png}}
    \subfloat[Autocorrelation of drag.]
    {\label{fig:pdf_drag_b}
    	\includegraphics[width=.45\linewidth]{./autocorr_drag/autocorr_drag.png}}  
      \caption{\textbf{(a)} Estimate of the zero-mean \ac{pdf} for drag fluctuations $f'_d = (f_d - \bar{f_d})$ where $\bar{f_d}$ denotes the averaged value. The drag is evaluated both in the presence and absence of the obstacle. Note that both \acsp{pdf} have different variance, and are here not normalized.
  \textbf{(b)} Autocorrelation function of the drag defined as $\left( \overline{f_d(t+\tau)f_d(t)}-\overline{f_d}^2 \right) /\sigma^2$. The lag $\tau$ is normalized by the turnover-time~\eqref{eq:turnover_time}.}
  \label{fig:pdf_drag}
\end{figure}
%
Lastly, the autocorrelation function of the drag is shown in Fig.~\ref{fig:pdf_drag_b}. It is found drag fluctuations are correlated over a time scale of the order of $\tau_0$, suggesting that the drag signal looses its memory typically after the sweeping of a few eddies past the obstacle.
%
This observation has important consequences for the application of rare event algorithms, as will be discussed in section~\ref{sec:rare_events_algorithms}.
%
In the following we define the \textit{correlation time} $\tau_c = 4\tau_0$.
Note that the ratio $tau_0 / tau_c$ may be viewed as a \textit{Strouhal number} $St$.
A value $St=0.25$ is consistent with commonly observed values for flows past blunt structures.
